### 2019-02-14 tex_v2/manuscript.tex
citations formatted

\begin{document}
	%word count: 156
	\begin{abstract}
		The acorn weevil snout exhibits remarkable flexibility and toughness that are derived from from the microarchitecture of its exoskeleton.
		Here we characterize modifications to the composite profile of the rostral cuticle that simultaneously enhance the flexibility and fracture toughness of the distal portion of the snout.
		Using Classical Laminate Plate Theory (CLPT) we estimate the effect of these modifications on the elastic behavior of the exoskeleton.
		Additionally, changes in the relative layer thicknesses and orientation angles of layers in the exoskeleton are related to the tensile behavior of the snout in six species of diverse morphology, and we demonstrate that a highly curved rostrum can be completely straightened without structural damage.
		We demonstrate that increased endocuticle thickness is strongly correlated with increased tensile strength in the snout.
		Consequently, snout stiffness is shown to be inversely correlated with fracture toughness.
		Finally, we identify exocuticle rich invaginations both as a likely site of crack initiation in tensile failure and as a source of morphological constraint on the evolution of the snout.

@@

	%word count:3486 - 71 = 3415
	{The exoskeleton of Coleoptera (beetles) is a hierarchically-structured fibrous composite characterized by variously arranged \textalpha-chitin (N-acetylglucosamine) nanofibrils embedded in a heterogeneous protein matrix.
	Although \textalpha-chitin is brittle and strongly anisotropic\unsure{give some numbers here}, beetle cuticle is simultaneously rigid and tough due to its unique laminate microstructure (see kamp, vincent for review), which we characterize in detail below.
	Impact-prone areas and exaggerated structures in arthropods generally exhibit cuticle organization that resists deformation and fracture; however, acorn weevils in the genus \textit{Curculio} Linnaeus, 1758\footnote{
		Pursuant to the International Code of Zoological Nomenclature, the first mention of any specific epithet will include the full genus and species names as a binomen (two part name) followed by the author and date of publication of the name.
		This is not an in-line reference; it is a part of the name itself and refers to a particular species-concept as indicated in the description of the species by that author.}
	instead exhibit unusual distal flexibility in an elongate extension of the head called the rostrum (snout).
	The rostrum is a hollow, strongly curved (over 90$\degree$ in some species), cylindrical, exoskeletal extension of the otherwise nearly-spherical head, which bears at its apex the terminal chewing mouthparts.
	This structure is used by the female to feed and to excavate sites for egg-laying (oviposition, see Fig.~1c), and can be repeatedly bent without evident damage despite being composed of the same material as other rigid body parts.
	By maintaining constant pressure on the snout and rotating around the bore-hole, females are able to flex the rostrum into a straightened configuration and produce a linear channel into the fruit; a single female may prepare hundreds of such sites as an adult.

	While this behavior has been observed in many species of \textit{Curculio}, it was unclear how the rostrum of female acorn weevils can withstand the repeated, often extreme bending incurred during the process of egg-chamber excavation.
	In this study we characterize the composite profile of the rostral cuticle to account for the observed flexibility of the snout.
	We show that the relative layer thicknesses and fiber orientation angles of the exocuticle and endocuticle of the rostrum are strongly differentiated from the head capsule and other body parts, and we estimate the effect of these differences on the elasticity of the cuticle using Classical Laminate Plate Theory (CLPT).
	Because recent studies have shown that the yield strength of the beetle exoskeleton is lower in tension than compression, we perform a comparative analysis of the ultimate tensile strength of the rostrum across species and snout morphotypes; we also report the results of displacement-controlled load cycling of the snout in a species with strongly curved morphology.
	We relate an observed increase in the volume fraction of endocuticle in the rostrum to higher tensile strength at the rostral apex in all tested species, and find that a strongly curved rostrum can be flexed repeatedly without harm to the structure.

	We additionally describe the fracture mechanics of the snout and consider how modification of the cuticle may prevent crack formation during oviposition.
	Based on our findings, we posit that the composite profile of the rostral apex enables the snout to undergo repeated distal flexion while remaining within the elastic limits of the material, mitigating the risk of structural damage, and without evident alteration of the mechanical properties of the individual components of the cuticle across the structure and between species.
	Thus, the flexibility and tensile strength of the rostrum appear to be derived \emph{exclusively} from modification of the composite architecture of the exoskeleton.
	To our knowledge, this is the first time that a modified composite profile has been reported as a means of enhancing structural elasticity in the insect exoskeleton.
}	
	\section{Microstructure of the \textit{Curculio} rostrum}
		In arthropods (including beetles), the exocuticle is comprised of numerous unidirectional laminae of chitin nanofibrils; each layer is the thickness of a single fiber (2-4\,nm) embedded in a proteinaceous matrix.
		These layers are stacked at a more or less constant angle to each other, forming a quasi-isotropic laminate known as the Bouligand structure \cite{Blackwell1980,Bouligand1972,Neville1976}. 
		This layout effectively mitigates the strong anisotropy of \textalpha-chitin to yield a versatile building material for the exoskeleton.		
		Beetle endocuticle, however, is unique among arthropods and is comprised of large (1-5\,{\textmu}m diameter) unidirectional bundles of chitin, called macrofibers.
		Chitin macrofibers are orthotropic (axial: $E_1~=~8.5\,\text{GPa}$, transverse: $ E_2~=~E_3~=~0.52\,\text{GPa}$ \cite{Jansen2016}) and arranged in unidirectional plies, seen in Figs.~REF \cite{Kamp2010,Kamp2015}.
		Typically, adjacent macrofiber laminae are paired and pseudo-orthogonal (i.e., angled approx. $90\degree$ to each other, see Figs.~REF), with a constant stacking angle \emph{between} pairs, although other configurations have been observed \cite{Hepburn1973,Kamp2010}.
		This geometric sequence of the macrofiber laminae yields an approximately transversely isotropic composite, similar to the Bouligand structure.
		Notably, the resulting laminate is less rigid than the exocuticle, but exhibits greater toughness because the pseudo-orthogonal plies effectively inhibit crack formation and propagation between successive layers \cite{Kamp2010,Kamp2015,Hepburn1973}.

@@

		We estimated the effect of differential cuticle organization on uni-axial membrane and transverse-flexural Young's moduli of the cuticle in the rostral apex and head capsule using Classical Laminate Plate Theory (CLPT), as detailed in our methods.
		The effective elastic constants of the cuticle regions of \textit{C.~longinasus} (estimated previously, see REF) were used to construct constitutive equations for the entire cuticle of that species.
		The cuticle of the head capsule was estimated to have membrane and flexural moduli of $E_m~=~4.77\,\text{GPa}$ and $E_f~=~6.04\,\text{GPa}$, respectively; however, in the rostral apex we found that these values were reduced by approximately 72\% and 60\%, respectively ($E_m~=~1.36\,\text{GPa}, E_f~=~2.44\,\text{GPa}$).
		Two hypothetical cuticle lay-ups were also modeled to individually assess the contributions of either modified layer thickness or stacking angle sequence to cuticle flexibility.
		The effective moduli of a configuration with the angle stacking sequence of typical cuticle (i.e., in the head capsule) but possessing the layer thicknesses of the rostral apex were calculated as $E_m~=~3.73\,\text{GPa}, E_f~=~4.31\,\text{GPa}$, representing 22\% and 29\% decreases from unmodified cuticle, respectively.
		Similarly, a hypothetical cuticle with the layer thicknesses of ordinary cuticle but possessing the angle stacking sequence of the rostral apex (i.e., $\pm45\degree$ angle-ply in the endocuticle) had effective elastic moduli of $E_m~=~3.77\,\text{GPa}, E_f~=~5.76\,\text{GPa}$, representing 21\% and 4.7\% decreases from unmodified cuticle, respectively.
		Each of the cuticle modifications noted in the rostral apex individually decreased the elastic moduli of the cuticle; however, they appear to have a synergistic combined effect on cuticle elasticity, rather than a simple additive effect.
		This result suggests that both modifications are necessary in order for the snout to function properly in the living animal, where the combined effect allows the rostrum to bend until completely straight without fracture.

	\section{Force-controlled loading to fracture}
		To better characterize the failure behavior of the rostrum, we performed tensile testing on the snouts of six \textit{Curculio} species that representing a mixture of closely and distantly related taxa (see Methods).
		Each specimen was immersed in $\text{di-H}_2\text{O}$ for 24 hours, to simulate the living tissue (see REFS), then subjected to force-controlled, uniaxial loading to fracture at a constant stress rate of $1.0\,\text{gf}\cdot\text{s}^{-1}$ (detailed in Methods).
		In general, the specimens exhibited a non-linear viscoelastic response curve characterized by a sharp increase in stress at higher strains, terminating in brittle fracture.
		We postulate that strain hardening occurs as the longitudinal axis of the macrofibers becomes more closely aligned to the cylindrical axis of the rostrum, thereby resisting tension more directly with increasing strain.

		We examined the correspondence between composite structure and mechanical behavior of the snout using phylogenetic linear mixed effects models (PGLMM) to account for phylogenetic non-independence in residual variance, with species membership included as a random effect.
		Our models show that the maximum force sustained at the site of failure was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle, at that site.
		Accordingly, there was a negative correlation between ultimate tensile strength of the specimen and the ratio of exocuticle to endocuticle cross-sectional area at the site of fracture.
		Although CLPT predicts a positive association between the proportion of exocuticle and stiffness of a generalized cuticle, we found no correspondence between the cross-sectional properties of the fracture site and the gross behavior of the entire rostrum.
		Because the cross-sectional areas of the cuticle regions vary across the length of the head along an anterior-posterior gradient, it is not possible to correlate measurements from the fracture surface to the properties of the entire snout.

		Instead, we found that the uniaxial elastic modulus (low strain: $E_{low}$) and secant modulus at failure ($E_{sec}$) were inversely correlated with ultimate strain and fracture toughness, implying that stiffer specimens, and by extension, stiffer cuticle profiles, are generally more brittle.
		We also observed a moderate, stiffening size-effect with respect to rostral length, contrary to our expectation that a longer, more strongly curved (REFS) snout would require increased flexibility to avoid fracture during oviposition.
		One possible explanation for this trend is that longer snouts may have a longer transition gradient from basal to apical profile to reinforce the junction between the rostrum and head capsule against buckling.
		Thus, Young's modulus of the rostrum would be comparatively higher in these species because of the higher volume fraction of exocuticle.
		From these tests, we infer that the gross elastic behavior of the cuticle is consistent across the genus, and that a single mechanism (i.e. the modified composite profile) confers increased flexibility and tensile strength to the rostral apex in the genus \textit{Curculio}.
		in agreement with our current understanding of cuticle mechanobiology.
		In addition, the endocuticle demonstrably contributes more to rostral tensile strength than the exocuticle, likely because of its organization into large bundles of aligned, anisotropic fibers, leading to a trade-off between rigidity and toughness.
		Consequently, the altered composite profile of the cuticle in the rostral apex makes the rostrum simultaneously more flexible and fracture resistant.

	\section{Load cycling of \textit{Curculio caryae}}
		To confirm that repeated, proscribed straightening of the rostrum does not result in damage to the cuticle, we performed displacement-controlled fatigue testing on a typical female specimen of \textit{Curculio caryae}, a species that exhibits extreme ($80-90\degree$) rostral curvature.
		The specimen was aligned so that uniaxial tension would induce elongation of the distal portion of the rostrum with minimal off-axis deflection of the un-curved section.
		The strain per cycle was fixed at an amplitude sufficient to completely elongate the snout and generate a tensile load of 1.0\,N  in the straightened configuration (ca. 20\% ultimate strength) at a frequency of $0.33\,\text{Hz}$.
		The test was terminated after a period of two weeks (ca.~400K cycles) when the stress amplitude appeared to reach an asymptotic minimum.		
		The rostrum behaved viscoelastically, indicated by histeresis in the stress-strain relationship during each cycle.
		Strain amplitude decreased logarithmically with cycle number, and the specimen initially appeared to have deformed plastically during the test.
		We believed that this indicated damage to the specimen; however, after cleaning the specimen in a 24 hour wash with ethanol and water, we observed that rostrum returned to its original shape.

		We cannot fully account for the stress relaxation of the rostrum after testing, but we speculate that it arose from the general mechanism associated with cuticle viscoelasticity.
		The endocuticle is made of aligned \textalpha-chitin nanofibrils whose crystalline structure is enforced by hydrogen bonds between individual chitin chains along their length; macroscopic viscoelastic behavior results from slippage between these chains as the hydrogen bonds break and reform in response to shearing between the chitin molecules.
		We posit that repeated strain may have caused such slippage in the endocuticle of the rostral apex during the fatigue test; however, without sufficient time for the material to \textit{completely} relax after deformation, the specimen would slowly accumulate strain and deform viscoelastically (REF-stress history dependence paper).
		After immersion in ethanol and water, the hydrogen bonds would relax sufficiently to allow the specimen to return to its original configuration, dissipating the accumulated strain.

@@

	\section{Fractography of test specimens}
	%word count: 653
		Although it was not always possible to identify void nucleation and crack initiation sites given the complex failure modes evident in the fractured specimens, we observed several patterns characteristic of both the micro-scale behavior of the cuticle and the meso-scale behavior of the rostrum during uniaxial tensile failure, which we describe here.

		In transverse view, the exocuticle consistently presented a nearly continuous fracture surface, characteristic of comparatively brittle failure, presumably due to the relatively homogeneous arrangement of \textalpha-chitin laminae in the Bouligand structure (REF).
		The exocuticle typically appeared to fracture at lower strains than the endocuticle, with shear-cusp formation evident both at the fracture surface and across exocuticle (but with endocuticle intact) adjacent to the plane of fracture.
		Conversely, the endocuticle exhibited severe delamination, off-axis ply-splitting, and fiber-pulling away from the fracture surface, indicating the relatively high toughness of the unidirectional \textalpha-chitin organization within the macrofibers (REF).
		Because the exocuticle of weevils is anchored to the endocuticle by cross-linking fibers, exocuticular shear-cusp formation in uniaxial tension suggests extension-shear coupling within individual endocuticle laminae, implying that ply-splitting occurred via mode II fracture between macrofibers at high strain.
		We Hypothesize that intra-laminar extension-shear coupling also yielded off-axis, in-plane resultant forces as a function of lamina orientation angle; mode III shearing then occurred between laminae with opposing in-plane resultant forces, causing the observed inter-ply delamination.
		Tensile failure of the macrofiber laminae would ultimately occur via mixed-mode I/II (transverse tension/intra-laminar shear) fracture due to an increase in applied stress caused by ply-splitting in adjacent laminae.

		At the meso-scale, most specimens fractured along a single plane across and between the occipital sulci, which are cuticle invaginations that traverse the entire length of the rostrum.
		These sulci increase the volume fraction of exocuticle in the ventral part of the snout and contain large interfaces ideal for void nucleation.
		The exocuticle of the occipital sulci usually displayed shear cusps oriented outward from the center of the invagination, continuing dorsolaterally and ventromedially.
		Ventrally the cusps converged toward a prominent scarp where the crack fronts joined, although in specimens with large cross-sectional areas of endocuticle, this was often obscured by delaminated endocuticular macrofibers.

@@

		From these patterns we hypothesize that the exocuticle-rich occipital sulci are the most likely site for the initiation of void nucleation and catastrophic failure of the integrated rostral cuticle in cross section, as illustrated in Fig~REF.
		According to this model, structural failure would take place as cracks propagate through the endocuticle from these sutures, which penetrate the entire thickness of the laminate.
		Although other, more complex failure modes have been observed, we posit that in live specimens this is the most likely mechanism of tensile failure because typical bending behavior generates tension only along the ventral surface of the rostrum.

	\section{Conclusions}
	%word count: 514 (3706 total)

		The rostrum of \textit{Curculio} is characterized by a discontinuous composite profile, wherein the cuticle is strongly differentiated in terms of relative layer thicknesses and orientation angles along an anterior-posterior gradient.		
		These modifications are sufficient to achieve marked reduction in the effective membrane and flexural moduli of the cuticle (72\% and 60\%, respectively) in constitutive models based on CLPT, thereby accounting for the observed flexibility of the rostral apex in live specimens.
		However, these reductions can only be realized with both modifications to the cuticle, which have a non-additive effect on cuticle elasticity, implying that these weevils require both modifications to function properly during oviposition.
		Likewise, tensile and fatigue testing have revealed a trade-off between stiffness and fracture resistance (as measured by ultimate strain and toughness), mediated by the relative proportion of endocuticle in the laminate.
		The altered composite profile of the cuticle in the rostral apex makes the rostrum simultaneously more flexible and fracture resistant, permitting the structure to be flexed without exceeding the elastic limits of the cuticle.
		To our knowledge, this is the first time that the composite profile of the cuticle has been related to a gradient in elasticity and tensile performance across a cuticular structure in arthropods.
		Because these associations were independent of species membership, we posit that the behavior of the cuticle is consistent across the genus, and that rostral flexibility is achieved exclusively through a modified cuticle lay-up in all \textit{Curculio} species.
		This conclusion raises the intriguing possibility that a single ancestral shift in cuticle organization at the rostral apex -- yielding higher flexibility and tensile strength -- opened a large region of morphospace for exploration, resulting in present day diversity of the genus.

>>>>

\begin{document}
	%word count: 156
	\begin{abstract}
		The acorn weevil snout exhibits remarkable flexibility and toughness that are derived from from the microarchitecture of its exoskeleton.
		Here we characterize modifications to the composite profile of the rostral cuticle that simultaneously enhance the flexibility and fracture toughness of the distal portion of the snout.
		Using Classical Laminate Plate Theory (CLPT) we estimate the effect of these modifications on the elastic behavior of the exoskeleton.
		Additionally, changes in the relative layer thicknesses and orientation angles of layers in the exoskeleton are related to the tensile behavior of the snout in six species of diverse morphology, and we demonstrate that a highly curved rostrum can be completely straightened without structural damage.
		We demonstrate that increased endocuticle thickness is strongly correlated with increased tensile strength in the snout.
		Consequently, snout stiffness is shown to be inversely correlated with fracture toughness.
		Finally, we identify exocuticle rich invaginations of the occipital sutures both as a likely site of crack initiation in tensile failure and as a source of morphological constraint on the evolution of the snout.

@@

	{The exoskeleton of Coleoptera (beetles) is a hierarchically-structured fibrous composite characterized by variously arranged \textalpha-chitin (N-acetylglucosamine) nanofibrils embedded in a heterogeneous protein matrix \cite{Hepburn1973, Jansen2016, Vincent2004}.
	Although \textalpha-chitin is brittle and strongly anisotropic, beetle cuticle is simultaneously rigid and tough due to its unique laminate microstructure (see kamp, vincent for review), which we characterize in detail below \cite{Kamp2010, Kamp2015, Neville1976}.
	Impact-prone areas and exaggerated structures in arthropods generally exhibit cuticle organization that resists deformation and fracture (e.g. \cite{Amini2015, Mccullough2014mech, Mccullough2014struc, Dirks2012, Dirks2013}); however, acorn weevils in the genus \textit{Curculio} Linnaeus, 1758\footnote{
		Pursuant to the International Code of Zoological Nomenclature, the first mention of any specific epithet will include the full genus and species names as a binomen (two part name) followed by the author and date of publication of the name.
		This is not an in-line reference; it is a part of the name itself and refers to a particular species-concept as indicated in the description of the species by that author \cite{ICZN1999}.}
	instead exhibit unusual distal flexibility in an elongate extension of the head called the rostrum (snout) \cite{Toju2005, Jansen2016, Singh2016, Gibson1969}.
	The rostrum is a hollow, strongly curved (over 90$\degree$ in some species), cylindrical, exoskeletal extension of the otherwise nearly-spherical head, which bears at its apex the terminal chewing mouthparts \cite{Morimoto2003, Ting1933, Ting1936, Dennell1942, Gibson1969}.
	This structure is used by the female to feed and to excavate sites for egg-laying (oviposition, see Fig.~1c), and can be repeatedly bent without evident damage despite being composed of the same material as other rigid body parts \cite{Jansen2016, Singh2016, Gibson1969, Toju2005}.
	By maintaining constant pressure on the snout and rotating around the bore-hole, females are able to flex the rostrum into a straightened configuration and produce a linear channel into the fruit; a single female may prepare hundreds of such sites as an adult \cite{Toju2005, Moffett1989, AguirreUribe1978}.

	While this behavior has been observed in many species of \textit{Curculio} \cite{Gibson1969, Moffett1989, AguirreUribe1978, Toju2005}, it was unclear how the rostrum of female acorn weevils can withstand the repeated, often extreme bending incurred during the process of egg-chamber excavation.
	In this study we characterize the composite profile of the rostral cuticle to account for the observed flexibility of the snout.
	We show that the relative layer thicknesses and fiber orientation angles of the exocuticle and endocuticle of the rostrum are strongly differentiated from the head capsule and other body parts, and we estimate the effect of these differences on the elasticity of the cuticle using Classical Laminate Plate Theory (CLPT).
	Because recent studies have shown that the yield strength of the beetle exoskeleton is lower in tension than compression \cite{Longhai2017}, we perform a comparative analysis of the ultimate tensile strength of the rostrum across species and snout morphotypes; we also report the results of displacement-controlled load cycling of the snout in a species with strongly curved morphology.
	We relate an observed increase in the volume fraction of endocuticle in the rostrum to higher tensile strength at the rostral apex in all tested species, and find that a strongly curved rostrum can be flexed repeatedly without harm to the structure.

	We additionally describe the fracture mechanics of the snout and consider how modification of the cuticle may prevent crack formation during oviposition.
	Based on our findings, we posit that the composite profile of the rostral apex enables the snout to undergo repeated distal flexion while remaining within the elastic limits of the material, mitigating the risk of structural damage, and without evident alteration of the mechanical properties of the individual components of the cuticle across the structure and between species.
	Thus, the flexibility and tensile strength of the rostrum appear to be derived \emph{exclusively} from modification of the composite architecture of the exoskeleton.
	To our knowledge, this is the first time that a modified composite profile has been reported as a means of enhancing structural elasticity in the insect exoskeleton (but see \cite{Matsumura2017}).
}	
	\section{Microstructure of the \textit{Curculio} rostrum}
		In arthropods (including beetles), the exocuticle is comprised of numerous unidirectional laminae of chitin nanofibrils; each layer is the thickness of a single fiber (2-4\,nm) embedded in a proteinaceous matrix \cite{Nikolov2010, Nikolov2011}.
		These layers are stacked at a more or less constant angle to each other, forming a quasi-isotropic laminate known as the Bouligand structure \cite{Blackwell1980, Bouligand1972, Neville1976}. 
		This layout effectively mitigates the strong anisotropy of \textalpha-chitin to yield a versatile building material for the exoskeleton \cite{Vincent1982, Vincent2004, Nikolov2010, Nikolov2011}.		
		Beetle endocuticle, however, is unique among arthropods and is comprised of large (1-5\,{\textmu}m diameter in \textit{Curculio}) unidirectional bundles of chitin, called macrofibers.
		Chitin macrofibers are orthotropic (axial: $E_1~=~8.5\,\text{GPa}$, transverse: $ E_2~=~E_3~=~0.52\,\text{GPa}$ \cite{Jansen2016}) and arranged in unidirectional plies, seen in Figs.~REF \cite{Kamp2010, Kamp2015}.
		Typically, adjacent macrofiber laminae are paired and pseudo-orthogonal (i.e., angled approx. $90\degree$ to each other \cite{Cheng2009}, see Figs.~REF), with a constant stacking angle \emph{between} pairs, although other configurations have been observed \cite{Hepburn1973, Kamp2010, Kamp2015, Leopold1992}.
		This geometric sequence of the macrofiber laminae yields an approximately transversely isotropic composite, similar to the Bouligand structure \cite{Kamp2015, Nikolov2010}.
		Notably, the resulting laminate is less rigid than the exocuticle, but exhibits greater toughness because the pseudo-orthogonal plies effectively inhibit crack formation and propagation between successive layers \cite{Kamp2010, Kamp2015, Hepburn1973}.

@@

		We estimated the effect of differential cuticle organization on uni-axial membrane and transverse-flexural Young's moduli of the cuticle in the rostral apex and head capsule using Classical Laminate Plate Theory (CLPT), as detailed in our methods \cite{Reddy2004, Jones2014}.
		The effective elastic constants of the cuticle regions of \textit{C.~longinasus} (estimated previously, see \cite{Jansen2016}) were used to construct constitutive equations for the entire cuticle of that species.
		The cuticle of the head capsule was estimated to have membrane and flexural moduli of $E_m~=~4.77\,\text{GPa}$ and $E_f~=~6.04\,\text{GPa}$, respectively; however, in the rostral apex we found that these values were reduced by approximately 72\% and 60\%, respectively ($E_m~=~1.36\,\text{GPa}, E_f~=~2.44\,\text{GPa}$).
		Two hypothetical cuticle lay-ups were also modeled to individually assess the contributions of either modified layer thickness or stacking angle sequence to cuticle flexibility.
		The effective moduli of a configuration with the angle stacking sequence of typical cuticle (i.e., in the head capsule) but possessing the layer thicknesses of the rostral apex were calculated as $E_m~=~3.73\,\text{GPa}, E_f~=~4.31\,\text{GPa}$, representing 22\% and 29\% decreases from unmodified cuticle, respectively.
		Similarly, a hypothetical cuticle with the layer thicknesses of ordinary cuticle but possessing the angle stacking sequence of the rostral apex (i.e., $\pm45\degree$ angle-ply in the endocuticle) had effective elastic moduli of $E_m~=~3.77\,\text{GPa}, E_f~=~5.76\,\text{GPa}$, representing 21\% and 4.7\% decreases from unmodified cuticle, respectively.
		Each of the cuticle modifications noted in the rostral apex individually decreased the elastic moduli of the cuticle; however, they appear to have a synergistic combined effect on cuticle elasticity, rather than a simple additive effect.
		This result suggests that both modifications are necessary in order for the snout to function properly in the living animal, where the combined effect allows the rostrum to bend until completely straight without fracture.

	\section{Force-controlled loading to fracture}
		To better characterize the failure behavior of the rostrum, we performed tensile testing on the snouts of six \textit{Curculio} species that representing a mixture of closely and distantly related taxa (see Methods) \cite{Hughes2004phylo, Hughes2004eco, Bonal2016, Bonal2011}.
		Each specimen was immersed in $\text{di-H}_2\text{O}$ for 24 hours, to simulate the living tissue (see \cite{Klocke2011}), then subjected to force-controlled, uniaxial loading to fracture at a constant stress rate of $1.0\,\text{gf}\cdot\text{s}^{-1}$ (detailed in Methods).
		In general, the specimens exhibited a non-linear viscoelastic response curve characterized by a sharp increase in stress at higher strains, terminating in brittle fracture \cite{Mihai2017}.
		We postulate that strain hardening occurs as the longitudinal axis of the macrofibers becomes more closely aligned to the cylindrical axis of the rostrum, thereby resisting tension more directly with increasing strain \cite{Munster2013}.

		We examined the correspondence between composite structure and mechanical behavior of the snout using phylogenetic linear mixed effects models (PGLMM) to account for phylogenetic non-independence in residual variance, with species membership included as a random effect \cite{Revell2010, Felsenstein1985}.
		Our models show that the maximum force sustained at the site of failure was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle, at that site.
		Accordingly, there was a negative correlation between ultimate tensile strength of the specimen and the ratio of exocuticle to endocuticle cross-sectional area at the site of fracture.
		Although CLPT predicts a positive association between the proportion of exocuticle and stiffness of a generalized cuticle, we found no correspondence between the cross-sectional properties of the fracture site and the gross behavior of the entire rostrum.
		Because the cross-sectional areas of the cuticle regions vary across the length of the head along an anterior-posterior gradient, it is not possible to correlate measurements from the fracture surface to the properties of the entire snout.

		Instead, we found that the uniaxial elastic modulus (low strain: $E_{low}$) and secant modulus at failure ($E_{sec}$) were inversely correlated with ultimate strain and fracture toughness, implying that stiffer specimens, and by extension, stiffer cuticle profiles, are generally more brittle.
		We also observed a moderate, stiffening size-effect with respect to rostral length, contrary to our expectation that a longer, more strongly curved (see \cite{Hughes2004eco, Bonal2011}) snout would require increased flexibility to avoid fracture during oviposition.
		One possible explanation for this trend is that longer snouts may have a longer transition gradient from basal to apical profile to reinforce the junction between the rostrum and head capsule against buckling.
		Thus, Young's modulus of the rostrum would be comparatively higher in these species because of the higher volume fraction of exocuticle.
		From these tests, we infer that the gross elastic behavior of the cuticle is consistent across the genus, and that a single mechanism (i.e. the modified composite profile) confers increased flexibility and tensile strength to the rostral apex in the genus \textit{Curculio}.
		In addition, the endocuticle demonstrably contributes more to rostral tensile strength than the exocuticle, likely because of its organization into large bundles of aligned, anisotropic fibers, leading to a trade-off between rigidity and toughness.
		Consequently, the altered composite profile of the cuticle in the rostral apex makes the rostrum simultaneously more flexible and fracture resistant.

	\section{Load cycling of \textit{Curculio caryae}}
		To confirm that repeated, proscribed straightening of the rostrum does not result in damage to the cuticle, we performed displacement-controlled fatigue testing on a typical female specimen of \textit{Curculio caryae}, a species that exhibits extreme ($80-90\degree$) rostral curvature \cite{AguirreUribe1978, Gibson1969}.
		The specimen was aligned so that uniaxial tension would induce elongation of the distal portion of the rostrum with minimal off-axis deflection of the un-curved section.
		The strain per cycle was fixed at an amplitude sufficient to completely elongate the snout and generate a tensile load of 1.0\,N  in the straightened configuration (ca. 20\% ultimate strength) at a frequency of $0.33\,\text{Hz}$.
		The test was terminated after a period of two weeks (ca.~400K cycles) when the stress amplitude appeared to reach an asymptotic minimum.		
		The rostrum behaved viscoelastically, indicated by histeresis in the stress-strain relationship during each cycle.
		Strain amplitude decreased logarithmically with cycle number, and the specimen initially appeared to have deformed plastically during the test.
		We believed that this indicated damage to the specimen; however, after cleaning the specimen in a 24 hour wash with ethanol and water, we observed that rostrum returned to its original shape.

		We cannot fully account for the stress relaxation of the rostrum after testing, but we speculate that it arose from the general mechanism associated with cuticle viscoelasticity.
		The endocuticle is made of aligned \textalpha-chitin nanofibrils whose crystalline structure is enforced by hydrogen bonds between individual chitin chains and with the protein matrix along their length; macroscopic viscoelastic behavior results from slippage between these chains in response to shearing between the chitin molecules \cite{Vincent2004, Evans1967, Sun2012}.
		We posit that repeated strain may have caused such slippage in the endocuticle of the rostral apex during the fatigue test; however, without sufficient time for the material to \textit{completely} relax after deformation, the specimen would slowly accumulate strain and deform viscoelastically \cite{Munster2013}.
		After immersion in ethanol and water, the cuticle would be sufficiently plasticized to allow the specimen to return to its original configuration, dissipating the accumulated strain.

@@

	\section{Fractography of test specimens}
		Although it was not always possible to identify void nucleation and crack initiation sites given the complex failure modes evident in the fractured specimens, we observed several patterns characteristic of both the micro-scale behavior of the cuticle and the meso-scale behavior of the rostrum during uniaxial tensile failure, which we describe here (see \cite{Greenhalgh2009} for general approach).

		In transverse view, the exocuticle consistently presented a nearly continuous fracture surface, characteristic of comparatively brittle failure, presumably due to the relatively homogeneous arrangement of \textalpha-chitin laminae in the Bouligand structure \cite{Nikolov2010, Nikolov2011}.
		The exocuticle typically appeared to fracture at lower strains than the endocuticle, with shear-cusp formation evident both at the fracture surface and across exocuticle (but with endocuticle intact) adjacent to the plane of fracture.
		Conversely, the endocuticle exhibited severe delamination, off-axis ply-splitting, and fiber-pulling away from the fracture surface, indicating the relatively high toughness of the unidirectional \textalpha-chitin organization within the macrofibers \cite{Kamp2010, Kamp2015}.
		Because the exocuticle of weevils is anchored to the endocuticle by cross-linking fibers (see \cite{Kamp2015, Longhai2017}), exocuticular shear-cusp formation in uniaxial tension suggests extension-shear coupling within individual endocuticle laminae, implying that ply-splitting occurred via mode II fracture between macrofibers at high strain \cite{Jones2014, Reddy2004}.
		We hypothesize that intra-laminar extension-shear coupling also yielded off-axis, in-plane resultant forces as a function of lamina orientation angle; mode III shearing then occurred between laminae with opposing in-plane resultant forces, causing the observed inter-ply delamination.
		Tensile failure of the macrofiber laminae would ultimately occur via mixed-mode I/II (transverse tension/intra-laminar shear) fracture due to an increase in applied stress caused by ply-splitting in adjacent laminae \cite{Greenhalgh2009}.

		At the meso-scale, most specimens fractured along a single plane across and between the occipital sulci, which are cuticle invaginations that traverse the entire length of the rostrum \cite{Davis2014, Dennell1942}.
		These sulci increase the volume fraction of exocuticle in the ventral part of the snout and contain large interfaces ideal for void nucleation.
		The exocuticle of the occipital sulci usually displayed shear cusps oriented outward from the center of the invagination, continuing dorsolaterally and ventromedially.
		Ventrally the cusps converged toward a prominent scarp where the crack fronts joined, although in specimens with large cross-sectional areas of endocuticle, this was often obscured by delaminated endocuticular macrofibers.

@@

		From these patterns we hypothesize that the exocuticle-rich occipital sulci are the most likely site for the initiation of void nucleation and catastrophic failure of the integrated rostral cuticle in cross section, as illustrated in Fig~REF.
		According to this model, structural failure would take place as cracks propagate through the endocuticle from these sutures, which penetrate the entire thickness of the laminate \cite{Davis2014}.
		Although other, more complex failure modes have been observed, we posit that in live specimens this is the most likely mechanism of tensile failure because typical bending behavior generates tension only along the ventral surface of the rostrum.

	\section{Conclusions}
		The rostrum of \textit{Curculio} is characterized by a discontinuous composite profile, wherein the cuticle is strongly differentiated in terms of relative layer thicknesses and orientation angles along an anterior-posterior gradient.		
		These modifications are sufficient to achieve marked reduction in the effective membrane and flexural moduli of the cuticle (72\% and 60\%, respectively) in constitutive models based on CLPT, thereby accounting for the observed flexibility of the rostral apex in live specimens.
		However, these reductions can only be realized with both modifications to the cuticle, which have a non-additive effect on cuticle elasticity, implying that these weevils require both modifications to function properly during oviposition.
		Likewise, tensile and fatigue testing have revealed a trade-off between stiffness and fracture resistance (as measured by ultimate strain and toughness), mediated by the relative proportion of endocuticle in the laminate.
		The altered composite profile of the cuticle in the rostral apex makes the rostrum simultaneously more flexible and fracture resistant, permitting the structure to be flexed without exceeding the elastic limits of the cuticle.
		To our knowledge, this is the first time that the composite profile of the cuticle has been related to a gradient in elasticity and tensile performance across a cuticular structure in arthropods.
		Because these associations were independent of species membership, we posit that the behavior of the cuticle is consistent across the genus, and that rostral flexibility is achieved exclusively through a modified cuticle lay-up in all \textit{Curculio} species.
		This conclusion raises the intriguing possibility that a single ancestral shift in cuticle organization at the rostral apex -- yielding higher flexibility and tensile strength -- opened a large region of morphospace for exploration, resulting in present day diversity of the genus.
